Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-09 hotstorage13/arch.tex
fix mark-sweep ref
w

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{snapshotdata.pdf}
\caption{ Metadata structure of a VM snapshot.}
\label{fig:snapshot}
\end{figure}
\subsection{Snapshot Representation}

@@

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.75\textwidth]{steps.pdf}
\caption{Processing flow in Phase 1 (VM scan/request accumulation) and Phase  2 (fingerprint comparison and duplicate summary output)
 for duplicate detection.}
\label{fig:flow}
\end{figure*}

\subsection{Processing flow and resource usage}
The data flow of our multi-phase duplicate detection is depicted in Figure~\ref{fig:flow}. 
%let $v$ be the total number of virtual machines hosted in  a cluster,  
%we divide the backup into $k$  iterations. 
%\begin{itemize}
%\item
The first phase is that each machine independently reads  
%$v/k$  
virtual machine images that need a backup
and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulates  into 
a partition bucket on the temporary disk storage. 
The partition mapping is using a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ parititons of content hash and accumulates corresponding requests on the disk. 
There are two options to assign buffers in each machine to buffer requests for each partition.
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers correspond to send requests to $p$ machines and 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests in each $p$ disk buffers to  $q$ local disk buffers,
and outputs each disk buffer to one of the request partitions on the disk
when this disk buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
much less disk seek overhead.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{snapshotdata.pdf}
\caption{ Metadata structure of a VM snapshot.}
\label{fig:snapshot}
\end{figure}
%\subsection{Snapshot Representation}

@@

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.75\textwidth]{steps.pdf}
\caption{Processing flow of Phases 1  and 2.}
\label{fig:flow}
\end{figure*}

%\subsection{Processing flow and resource usage}
The data flow of our multi-phase duplicate detection is depicted in Figure~\ref{fig:flow}. 
%let $v$ be the total number of virtual machines hosted in  a cluster,  
%we divide the backup into $k$  iterations. 
%\begin{itemize}
%\item
The first phase is that each machine independently reads  
%$v/k$  
virtual machine images that need a backup
and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulates  into 
a partition bucket on the temporary disk storage. 
The partition mapping is using a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ parititons of content hash and accumulates corresponding requests on the disk. 
There are two options to assign buffers in each machine to buffer requests for each partition.
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers correspond to send requests to $p$ machines and 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests in each $p$ disk buffers to  $q$ local disk buffers,
and outputs each disk buffer to one of the request partitions on the disk
when this disk buffer becomes full.  Option 2 is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
much less disk seek overhead.

### 2013-03-09 hotstorage13/eval.tex
w

\subsection{Experimental setup}

@@

\begin{table}[hbt]
\caption{ Performance of multi-phase backup with deduplication.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
\hline Index+request & 161&  29 & 17.9 & 10.7 & 5.3 \\
  (MB)           &  &   &  & &  \\

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{mem_time.pdf}
\caption{ Parallel time when memory limit imposed varies from 20MB to 200MB.}
\label{fig:memory}
\end{figure}

Figure~\ref{tab:memory} shows the performance data when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
Each scan takes about 1.4 hours.
Using about 30MB is sufficient to have VM backup completed in parallel 
within about 3.09 hours.

>>>>

%\subsection{Experimental setup}

@@

\begin{table}[hbt]
\caption{ Performance of multi-phase deduplication.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions  & 50 & 275  &450 &  750 &  1500 \\
\hline Index+request & 161&  29 & 17.9 & 10.7 & 5.3 \\
  (MB)           &  &   &  & &  \\

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{mem_time.pdf}
\caption{ Parallel time when memory limit varies.}
\label{fig:memory}
\end{figure}

Figure~\ref{fig:memory} shows the performance data when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
Each scan takes about 1.4 hours.
Using about 30MB is sufficient to have VM backup completed in parallel 
within about 3.09 hours.
